Do music charts still matter in the streaming age? An analysis predicting Beyoncé’s Spotify numbers using a regression model.

### 2024-04-17 paper/paper.qmd
Add title to paper and README

---
title: "Beyoncé"
author: Tam Ly
thanks: "Code and data are available at: [https://github.com/atn-ly/beyonce](https://github.com/atn-ly/beyonce)"
date: today
date-format: long
abstract: "This paper analyzes the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100* utilizing data collected from Spotify and Billboard. We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases. Our discovery highlights the relevance of charts in shaping today’s music industry."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Do music charts still matter in the streaming age? An analysis predicting Beyoncé’s Spotify numbers using a regression model."
author: Tam Ly
thanks: "Code and data are available at: [https://github.com/atn-ly/beyonce](https://github.com/atn-ly/beyonce)"
date: today
date-format: long
abstract: "This paper analyzes the number of Spotify streams of a Beyoncé song based on the number of weeks it spent on the *Billboard Hot 100* utilizing data collected from Spotify and Billboard. We find that the number of Spotify streams of a Beyoncé song increases as its duration on the *Billboard Hot 100* increases. Our discovery highlights the relevance of charts in shaping today’s music industry."
format: pdf
number-sections: true
bibliography: references.bib
---
